---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - First author
  - Another author
thanks: "Code and data are available at: LINK."
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
output:
  bookdown::pdf_document2
toc: FALSE
bibliography: references.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(palmerpenguins)
library(scales)
data <- readr::read_csv("../data/cleaned_data.csv")
```

# Introduction

You can and should cross-reference sections and sub-sections. For instance, Section \@ref(data). R Markdown automatically makes the sections lower case and adds a dash to spaces to generate labels, for instance, Section \@ref(first-discussion-point). 



# Data

Our data is of penguins (Figure \@ref(fig:bills)).

```{r bills, fig.cap="Bills of penguins", echo = FALSE}
age_group_diverging <- data %>% filter(demographic_type == "age group" ,survey_answer != "don't know")%>% mutate(chances_of_getting_aids = if_else(survey_answer %in% c("no risk at all","small"), -chances_of_getting_aids, chances_of_getting_aids)) %>%
  mutate(percent_label = abs(chances_of_getting_aids)) %>%
  mutate(percent_label = percent(chances_of_getting_aids/100, accuracy = 1))

age_group_diverging %>% filter(gender == "male")%>%
  ggplot(aes(
    x = demographic_info,
    y = chances_of_getting_aids,
    fill = survey_answer
  )) + geom_col() +
  geom_text(aes(label = percent_label),
    position = position_stack(vjust = 0.5),
    color = "white",
    fontface = "bold"
  ) +
  coord_flip() +
  scale_x_discrete() +
  scale_fill_manual(
    breaks = c("no risk at all", "small", "moderate", "great"),
    values = c(
      "no risk at all" = "darkslategray4",
      "small" = "darkslategray2",
      "moderate" = "deepskyblue2",
      "great" = "deepskyblue4"
    )
  ) +
  labs(
    title = "What is your chances of getting AIDS?",
    x = "age group",
    fill = NULL
  ) +
  theme_minimal() +
  theme(
    axis.title.y = element_text(margin = margin(r = 20)),
    axis.text.x = element_blank(),
    axis.title.x = element_blank(),
    panel.grid = element_blank(),
    legend.position = "top"
  )
  
  age_group_diverging %>% filter(gender == "female")%>%
  ggplot(aes(
    x = demographic_info,
    y = chances_of_getting_aids,
    fill = survey_answer
  )) + geom_col() +
  geom_text(aes(label = percent_label),
    position = position_stack(vjust = 0.5),
    color = "white",
    fontface = "bold"
  ) +
  coord_flip() +
  scale_x_discrete() +
  scale_fill_manual(
    breaks = c("no risk at all", "small", "moderate", "great"),
    values = c(
      "no risk at all" = "pink4",
      "small" = "pink2",
      "moderate" = "brown2",
      "great" = "brown4"
    )
  ) +
  labs(
    title = "What is your chances of getting AIDS?",
    x = "age group",
    fill = NULL
  ) +
  theme_minimal() +
  theme(
    axis.title.y = element_text(margin = margin(r = 20)),
    axis.text.x = element_blank(),
    axis.title.x = element_blank(),
    panel.grid = element_blank(),
    legend.position = "top"
  )
```

Talk more about it.

Also bills and their average (Figure \@ref(fig:billssssss)). (Notice how you can change the height and width so they don't take the whole page?)

```{r billssssss, fig.cap="More bills of penguins", echo = FALSE, fig.width=8, fig.height=4}

# This needs to be about the random data tha tI sasmpled?
ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(alpha = 0.8) +
  scale_fill_manual(
    values = c("darkorange", "purple", "cyan4"),
    guide = FALSE
  ) +
  theme_minimal() +
  facet_wrap(~species, ncol = 1) +
  coord_flip()
```

Talk way more about it. 



# Model

\begin{equation}
Pr(\theta | y) = \frac{Pr(y | \theta) Pr(\theta)}{Pr(y)}  (\#eq:bayes)
\end{equation}

Equation \@ref(eq:bayes) seems useful, eh?

Here's a dumb example of how to use some references: In paper we run our analysis in `R` [@citeR]. We also use the `tidyverse` which was written by @thereferencecanbewhatever If we were interested in baseball data then @citeLahman could be useful. 

We can use maths by including latex between dollar signs, for instance $\theta$.


# Results

# Discussion

## First discussion point

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this. 

## Second discussion point

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {-}


# Additional details


\newpage


# References
